Draft Report

### 2020-11-17 DraftReport.Rmd
Updated the draft report with meeting discussions

# Transform the variable by taking the logarithm and assign it to a new variable
df <- df %>% 
  mutate(l_population_density = log(population_density))

@@

```{r}
model1 <- lm(case_rate_100k ~ log(population_density) , data = df)
coeftest(model1, vcov = vcovHC)
```

@@

```{r}
df %>% 
  ggplot(aes(log(population_density), case_rate_100k, color = White...of.Total.Population)) + 
  geom_point() +   
  labs(
    title = 'Relation of Case.Rate.per.100000 to Population Density', 
    x = 'Log Population Density', 
    y = 'Case.Rate.per.100000',
    color = 'White %'
  )
```
```{r}
df %>% 
  ggplot(aes(x = log(population_density), y = case_rate_100k, color = Percent.living.under.the.federal.poverty.line..2018.)) + 
  geom_point() +   
  labs(
    title = 'Relation of Case.Rate.per.100000 to Population Density', 
    x = 'log Population Density', 
    y = 'Case.Rate.per.100000',
    color = 'Poverty Percentage'
  )
```

@@

```{r}
df %>% 
  ggplot(aes(x = Percent.living.under.the.federal.poverty.line..2018., y = case_rate_100k, color = log(population_density))) + 
  geom_point() +   
  labs(
    title = 'Relation of Case.Rate.per.100000 to Poverty %', 
    x = 'Percent.living.under.the.federal.poverty.line..2018.', 
    y = 'Case.Rate.per.100000',
    color = 'log(Population Density)'
  )
```
```{r}
df %>% 
  ggplot(aes(X65., case_rate_100k, color = log(population_density))) + 
  geom_point() +   
  labs(
    title = 'Relation of Case.Rate.per.100000 to 65+ Percentage', 
    x = 'X65+.', 
    y = 'Case.Rate.per.100000',
    color = 'log(Population density)'
  )
```

```{r}
df %>% 
  ggplot(aes(Percent.Unemployed..2018., case_rate_100k, color = log(population_density))) + 
  geom_point() +   
  labs(
    title = 'Relation of Case.Rate.per.100000 to Unemployed Percentage', 
    x = 'Percent.Unemployed..2018.', 
    y = 'Case.Rate.per.100000',
    color = 'log(Population density)'
  )
```

@@

```{r}
model2a <- lm(case_rate_100k ~ log(population_density)+ White...of.Total.Population, data = df)
coeftest(model2a, vcov = vcovHC)

@@

$$
\begin{aligned}
 Case.Rate.Per.100000 &=\beta_0 +\beta_1 log(Population.Density.Per.Square.Miles)\\ &+ \beta_2(White.Percentage.of.total. population)^2
\end{aligned}
$$
```{r}
model2a <- lm(case_rate_100k ~ log(population_density)+ I((White...of.Total.Population)^2), data = df)
coeftest(model2a, vcov = vcovHC)
```
$$
\begin{aligned}
 Case.Rate.Per.100000 &=\beta_0 + \beta_2(White.Percentage.of.total. population)^2
\end{aligned}
$$
```{r}
model2a <- lm(case_rate_100k ~ I((White...of.Total.Population)^2), data = df)
coeftest(model2a, vcov = vcovHC)
```

#### Model 2-b
$$
\begin{aligned}
 Case.Rate.Per.100000 &=\beta_0 +\beta_1 log(Population.Density.Per.Square.Miles)\\ &+ \beta_2(White.Percentage.of.total. population)\\ &+\beta_3(Percen.living.under.the.federal.poverty.line.2018)
\end{aligned}
$$

```{r}
model2bi <- lm(case_rate_100k ~log(population_density)+ white_pct+Percent.living.under.the.federal.poverty.line..2018., data = df)
coeftest(model2bi, vcov = vcovHC)
```

$$
\begin{aligned}
 Case.Rate.Per.100000 &=\beta_0 +\beta_1 log(Population.Density.Per.Square.Miles)\\ &+ \beta_2(White.Percentage.of.total. population)^2\\ &+\beta_3(Percen.living.under.the.federal.poverty.line.2018)
\end{aligned}
$$
```{r}
model2bii <- lm(case_rate_100k ~log(population_density)+ I((White...of.Total.Population)^2) + Percent.living.under.the.federal.poverty.line..2018., data = df)
coeftest(model2bii, vcov = vcovHC)
```
$$
\begin{aligned}
 Case.Rate.Per.100000 &=\beta_0 +\beta_3(Percen.living.under.the.federal.poverty.line.2018)
\end{aligned}
$$
```{r}
model2biii <- lm(case_rate_100k ~ Percent.living.under.the.federal.poverty.line..2018., data = df)
coeftest(model2biii, vcov = vcovHC)
```

@@

$$
\begin{aligned}
 Case.Rate.Per.100000 &=\beta_0 +\beta_1 log(Population.Density.Per.Square.Miles)\\ &+ \beta_2(White.Percentage.of.total. population)^2\\ &+\beta_4(Percent.Unemployed..2018.)
\end{aligned}
$$
```{r}
model2c <- lm(case_rate_100k ~log(population_density)+ I((White...of.Total.Population)^2) + Percent.Unemployed..2018., data = df)
coeftest(model2c, vcov = vcovHC)

```
$$
\begin{aligned}
 Case.Rate.Per.100000 &=\beta_0+\beta_4(Percent.Unemployed..2018.)
\end{aligned}
$$
```{r}
model2c <- lm(case_rate_100k ~ Percent.Unemployed..2018., data = df)
coeftest(model2c, vcov = vcovHC)
```

@@

$$
\begin{aligned}
Case.Rate.Per.100000=\beta_0 &+\beta_1log(Population.Density.Per.Square.Miles)\\&+\beta_2(White.Percentage.of.total.population)\\&+\beta_3(Percen.living.under.the.federal.poverty.line.2018)\\&+\beta_5(65+)
\end{aligned}
$$
```{r}
model2d <- lm(case_rate_100k ~log(population_density)+ White...of.Total.Population+Percent.living.under.the.federal.poverty.line..2018.+X65., data = df)
coeftest(model2d, vcov = vcovHC)
```

$$
\begin{aligned}
Case.Rate.Per.100000=\beta_0 &+\beta_1log(Population.Density.Per.Square.Miles)\\&+\beta_2(White.Percentage.of.total.population)^2\\&+\beta_3(Percen.living.under.the.federal.poverty.line.2018)\\&+\beta_4(65+)
\end{aligned}
$$
```{r}
model2d <- lm(case_rate_100k ~log(population_density)+ I((White...of.Total.Population)^2) + Percent.living.under.the.federal.poverty.line..2018.+X65., data = df)
coeftest(model2d, vcov = vcovHC)
```

$$
\begin{aligned}
Case.Rate.Per.100000=\beta_0+\beta_4(65+)
\end{aligned}
$$
```{r}
model2d <- lm(case_rate_100k ~X65., data = df)
coeftest(model2d, vcov = vcovHC)
```

@@

```{r}
model3a <- lm(case_rate_100k ~ log(population_density) + white_pct 
              + Percent.living.under.the.federal.poverty.line..2018.
              + mask_public_bool, data = df)
coeftest(model3a, vcov = vcovHC)
```
#### Model 3-b&c
Considering that there could be multiple policy variables that are relevant to predicting the case number. We have also examined the "Closed.other.non.essential.businesses" variable (renamed as "business_closed") which represents the date when the state issued closure of non-essential businesses. As "business_closed" is a date variable, a transformation was performed to convert the date into a variable "business_close_diff" which represents the days difference between the business close date of the state compared to the average date of all the states.
```{r}

@@

```{r warning=FALSE}
se.model1 = coeftest(model1, vcov = vcovHC)[ , "Std. Error"]
se.model2 = coeftest(model2bi, vcov = vcovHC)[ , "Std. Error"]
#se.model3 = coeftest(model2b, vcov = vcovHC)[ , "Std. Error"]
#se.model4 = coeftest(model2c, vcov = vcovHC)[ , "Std. Error"]
#se.model5 = coeftest(model2d, vcov = vcovHC)[ , "Std. Error"]
se.model6 = coeftest(model3a, vcov = vcovHC)[ , "Std. Error"]

stargazer(model1, model2bi, model3a, type = "text", omit.stat = "f",
          se = list(se.model6),
          star.cutoffs = c(0.05, 0.01, 0.001), title = "Table 1: The relationship between COVID case rate and population density")

@@

>>>>

# Transform the variable by taking the logarithm and assign it to a new variable
df <- df %>% 
  mutate(l_population_density = log10(population_density))

@@

```{r}
model1 <- lm(case_rate_100k ~ log10(population_density) , data = df)
coeftest(model1, vcov = vcovHC)
```

@@

```{r}
df %>% 
  ggplot(aes(log10(population_density), case_rate_100k, color = White...of.Total.Population)) + 
  geom_point() +   
  labs(
    title = 'Relation of Case.Rate.per.100000 to Population Density', 
    x = 'Log Population Density', 
    y = 'Case.Rate.per.100000',
    color = 'White %'
  )
```
```{r}
df %>% 
  ggplot(aes(x = log10(population_density), y = case_rate_100k, color = Percent.living.under.the.federal.poverty.line..2018.)) + 
  geom_point() +   
  labs(
    title = 'Relation of Case.Rate.per.100000 to Population Density', 
    x = 'log Population Density', 
    y = 'Case.Rate.per.100000',
    color = 'Poverty Percentage'
  )
```

@@

```{r}
df %>% 
  ggplot(aes(x = Percent.living.under.the.federal.poverty.line..2018., y = case_rate_100k, color = log10(population_density))) + 
  geom_point() +   
  labs(
    title = 'Relation of Case.Rate.per.100000 to Poverty %', 
    x = 'Percent.living.under.the.federal.poverty.line..2018.', 
    y = 'Case.Rate.per.100000',
    color = 'log(Population Density)'
  )
```
```{r}
df %>% 
  ggplot(aes(X65., case_rate_100k, color = log10(population_density))) + 
  geom_point() +   
  labs(
    title = 'Relation of Case.Rate.per.100000 to 65+ Percentage', 
    x = 'X65+.', 
    y = 'Case.Rate.per.100000',
    color = 'log(Population density)'
  )
```

```{r}
df %>% 
  ggplot(aes(Percent.Unemployed..2018., case_rate_100k, color = log10(population_density))) + 
  geom_point() +   
  labs(
    title = 'Relation of Case.Rate.per.100000 to Unemployed Percentage', 
    x = 'Percent.Unemployed..2018.', 
    y = 'Case.Rate.per.100000',
    color = 'log(Population density)'
  )
```

@@

```{r}
model2a <- lm(case_rate_100k ~ log10(population_density)+ White...of.Total.Population, data = df)
coeftest(model2a, vcov = vcovHC)

@@

$$
\begin{aligned}
 Case.Rate.Per.100000 &=\beta_0 +\beta_1 log(Population.Density.Per.Square.Miles)\\ &+ \beta_2(White.Percentage.of.total. population)^2
\end{aligned}
$$
```{r}
model2a <- lm(case_rate_100k ~ log10(population_density)+ I((White...of.Total.Population)^2), data = df)
coeftest(model2a, vcov = vcovHC)
```

#### Model 2-b

$$
\begin{aligned}
 Case.Rate.Per.100000 &=\beta_0 +\beta_1 log(Population.Density.Per.Square.Miles) + \beta_3(Percen.living.under.the.federal.poverty.line.2018)
\end{aligned}
$$
```{r}
model2b <- lm(case_rate_100k ~ log10(population_density) + Percent.living.under.the.federal.poverty.line..2018., data = df)
coeftest(model2b, vcov = vcovHC)
```

@@

$$
\begin{aligned}
 Case.Rate.Per.100000 &=\beta_0+\beta_1 log(Population.Density.Per.Square.Miles)+\beta_4(Percent.Unemployed..2018.)
\end{aligned}
$$
```{r}
model2c <- lm(case_rate_100k ~ log10(population_density) + Percent.Unemployed..2018., data = df)
coeftest(model2c, vcov = vcovHC)
```

@@

$$
\begin{aligned}
Case.Rate.Per.100000=\beta_0+\beta_1log(Population.Density.Per.Square.Miles)+\beta_4(65+)
\end{aligned}
$$
```{r}
model2d <- lm(case_rate_100k ~log10(population_density)+ X65., data = df)
coeftest(model2d, vcov = vcovHC)
```

@@

```{r}
model3a <- lm(case_rate_100k ~ log10(population_density)
              + Percent.living.under.the.federal.poverty.line..2018.
              + mask_public_bool, data = df)
coeftest(model3a, vcov = vcovHC)
```
#### Model 3-b&c
Considering that there could be multiple policy variables that are relevant to predicting the case number. We have also examined the "Closed.other.non.essential.businesses" variable (renamed as "business_closed") which represents the date when the state issued closure of non-essential businesses. As "business_closed" is a date variable, a transformation was performed to convert the date into a variable "business_close_diff" which represents the days difference between the business close date of the state compared to the average date of all the states.
```{r}

@@

```{r warning=FALSE}
se.model1 = coeftest(model1, vcov = vcovHC)[ , "Std. Error"]
se.model2 = coeftest(model2b, vcov = vcovHC)[ , "Std. Error"]
se.model3 = coeftest(model3a, vcov = vcovHC)[ , "Std. Error"]

stargazer(model1, model2b, model3a, type = "text", omit.stat = "f",
          se = list(se.model3),
          star.cutoffs = c(0.05, 0.01, 0.001), title = "Table 1: The relationship between COVID case rate and population density")

@@

- Discuss variables included and not included in the model
- Talk about Adjusted R2
- Talk about significant variables in the table
- Provide a statement that the table may change in the final report with more variables and maybe different key variables (case rate and population density)
